\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-18 cover-letter/cover-letter-resubmit.tex
Update cover letter

We have heavily revised the manuscript, substantially shortening it
and moving some more technical and descriptive section to appendices.
We have attached a detailed point-by-point response in the 
\texttt{response-to-reviewers.pdf} file, along with a 
latex-diff of the differences between the current and previous submissions.

Given your influence on the manuscript, we have included you in the
Acknowledgements, and thank you again for taking the time to give
such thoughtful and detailed feedback.

>>>>

We have heavily revised the manuscript, substantially shortening it
and moving some more technical and descriptive sections to appendices.
We have attached a detailed point-by-point response in the 
\texttt{response-to-reviewers.pdf} file, along with a 
latex-diff of the differences between the current and previous submissions.

Given your major influence on the manuscript, we have included you in the
Acknowledgements, and thank you again for taking the time to give
such helpful, thoughtful and detailed feedback.
